---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 6,
  fig.retina = 3,
  out.width = "100%"
)
```

# ggsegSUIT

> **Work in Progress** — This package is under active development and has not yet been officially released.

SUIT cerebellar lobular atlas for the ggseg ecosystem.

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ggseg/ggsegSUIT")
```

## SUIT atlas
```{r "suit"}
library(ggseg)
library(ggsegSUIT)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = suit(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = suit()$palette, na.value = "grey") +
  theme_void() +
  ggtitle("SUIT cerebellar lobular atlas")
```

## Reference

Diedrichsen J et al. (2009). A probabilistic MR atlas of the human
cerebellum. *NeuroImage*, 46(1), 39-46.

## Code of Conduct

Please note that the ggsegSUIT project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this
project, you agree to abide by its terms.
